Design of Adaptive Constellations and Error Protection Coding for Wireless Network Coding in 5-node Butterfly Networks

### 2016-12-23 Const_design.tex
Prerelease

%% LyX 2.1.5 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.
\documentclass[letterpaper,english,10pt]{bmc_template/bmcart}
\usepackage{mathptmx}
\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
\usepackage{array}
\usepackage{float}
\usepackage{units}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[dvips]{graphicx}
\usepackage{setspace}
\usepackage{wasysym}
\usepackage{nomencl}
% the following is useful when we have the old nomencl.sty package
\providecommand{\printnomenclature}{\printglossary}
\providecommand{\makenomenclature}{\makeglossary}
\makenomenclature
\doublespacing

@@

We assume a \emph{symmetric} WBN model \cite{Uricar-Qian-Sykora-Mow_2013-WCNC,Uricar-Qian-Sykora-Mow_2014-IEEE-T-WC}
with a half-duplex constraint (Fig. \ref{fig:CTUpp_Information_flows}).
An example practical scenario complying with the WBN model is a communication
among vehicles and road-side infrastructure nodes for traffic information
exchange on a bidirectional highway within two time slots \cite{Ho-Liew-Lu}.
The direct channels between the intended source$\rightarrow$destination
pairs are not available in WBN and thus the help of the intermediate
relay node is necessary to enable end-to-end communication. Please
note that in this paper we do not limit our attention to the above
mentioned special example of a high-speed, vehicle-based WBN.

@@

\begin{itemize}
\item $\left[\mathbf{d}_{A}^{s};\mathbf{d}_{B}^{s};f(\mathbf{d}_{A}^{b},\mathbf{d}_{B}^{b})\right]$
(from the relay signal (\ref{eq:CTUpp_relay_output}))
\item $\mathbf{d}_{i}^{b}$ (from the stored signal $z_{j}$ (\ref{eq:CTUpp_Dj_received}),
after interference cancellation (IC) of known $\mathbf{d}_{i}^{s}$)
\item $\mathbf{d}_{j}^{b}$ (from $\mathbf{d}_{i}^{b}$ and $f(\mathbf{d}_{A}^{b},\mathbf{d}_{B}^{b})$,
using a standard WNC decoding \cite{Sykora-Burr_2011-TVT})
\end{itemize}
\item $D_{j}$ merges $\mathbf{d}_{j}^{b}$ with $\mathbf{d}_{j}^{s}$ to
obtain the desired $\left[\mathbf{d}_{j}^{b};\mathbf{d}_{j}^{s}\right]$.\end{itemize}
\tabularnewline
\hline 
\end{tabular}vskip1ex\caption{SC-based relaying scheme in uncoded WBN}.\label{tab:CTUpp_SC-relaying-scheme}
\end{table}

@@

\section*{Availability of Data and Materials}

>>>>

%% LyX 2.1.5 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.
\documentclass[letterpaper,english,10pt]{bmc_template/bmcart}
\usepackage{mathptmx}
\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
\usepackage{array}
\usepackage{float}
\usepackage{units}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[dvips]{graphicx}
\usepackage{setspace}
\usepackage{wasysym}
\usepackage{nomencl}
\usepackage{url}
% the following is useful when we have the old nomencl.sty package
\providecommand{\printnomenclature}{\printglossary}
\providecommand{\makenomenclature}{\makeglossary}
\makenomenclature
\doublespacing

@@

We assume a \emph{symmetric} WBN model \cite{Uricar-Qian-Sykora-Mow_2013-WCNC,Uricar-Qian-Sykora-Mow_2014-IEEE-T-WC}
with a half-duplex constraint (Fig. \ref{fig:CTUpp_Information_flows}).
An example practical scenario complying with the WBN model is a communication
among vehicles and road-side infrastructure nodes for traffic information
exchange on a bidirectional highway within two time slots \cite{Ho-Liew-Lu}.
The direct channels between the intended source$\rightarrow$destination
pairs are not available in WBN and thus the help of the intermediate
relay node is necessary to enable end-to-end communication. Note that some partial 
source material from the implementation of this model can be found in
\cite{Prochazka_Tutorial_WNC}.

@@

\begin{itemize}
\item $\left[\mathbf{d}_{A}^{s};\mathbf{d}_{B}^{s};f(\mathbf{d}_{A}^{b},\mathbf{d}_{B}^{b})\right]$
(from the relay signal (\ref{eq:CTUpp_relay_output}))
\item $\mathbf{d}_{i}^{b}$ (from the stored signal $z_{j}$ (\ref{eq:CTUpp_Dj_received}),
after interference cancellation (IC) of known $\mathbf{d}_{i}^{s}$)
\item $\mathbf{d}_{j}^{b}$ (from $\mathbf{d}_{i}^{b}$ and $f(\mathbf{d}_{A}^{b},\mathbf{d}_{B}^{b})$,
using a standard WNC decoding \cite{Sykora-Burr_2011-TVT})
\end{itemize}
\item $D_{j}$ merges $\mathbf{d}_{j}^{b}$ with $\mathbf{d}_{j}^{s}$ to
obtain the desired $\left[\mathbf{d}_{j}^{b};\mathbf{d}_{j}^{s}\right]$.\end{itemize}
\tabularnewline
\hline 
\end{tabular}\caption{SC-based relaying scheme in uncoded WBN}.\label{tab:CTUpp_SC-relaying-scheme}
\end{table}

@@

\section*{Availability of Data and Materials}
We are aware that the presented topic is difficult to understand without very specific background in wireless
network coding. To help the reader to overcame this problem, we created a short tutorial \cite{Prochazka_Tutorial_WNC}.
The tutorial first motivates the constellation design, then it shortly introduces the wireless
network coding principle, its relation to conventional network coding. Many visual demonstrations of
the proposed constellation design can be also found there. In addition to this, the supplementary
Python code is available to the reader so that one can touch the topic also by means of implemented
algorithms.
